A demonstration of the \LaTeXe\ class file for \itshape{\journalnamelc}\footnotemark[2]

### 2019-09-21 journal/conclusions.tex
much more

\section{Conclusions and Future Work}
\label{conc}
When are two failing test cases due to the same fault?  This paper
demonstrates that
``when they are repaired by the same program mutants'' is a useful answer to
this question.  The problem of causality in executions is hard, and
has long been tied to a notion of similarity of
executions \cite{NearNeighbor,GroceError}.  By using program changes
(produced by mutants) as
causes to determine distance, it is possible to improve on efforts
to identify the set of faults in a large set of redundant compiler failures
\cite{PLDI13} and discover the source code locations of faults
\cite{MUSE,multilingual}.  For a set of more than 2,800 tests and more
than 50 faults, over the Mozilla SpiderMonkey 1.6 JavaScript compiler and
GCC 4.3.0, our methods improve fault identification (``fuzzer taming''), in a statistically significant way
(with effect size of about 3\% improvement), over
the \emph{best} (for each subject program) of over 16 metrics considered in previous work.
Preliminary investigation also shows improvement (for a shared
mutation testing budget) over previous mutant-based fault localization
methods, for the same tests and a subset of 24 faults with known
locations.  Our {\bf Repair} method, in particular, was the only
localization approach to provide any perfect localizations of faults
(it produced 3),
and provided three times as many very-high-quality (ranking the fault
in top 5 locations) localizations as the next best method
\cite{multilingual}  --- 6 such localizations, compared to only 2.
For GCC wrong-code faults, only our methods produced any
very-high-quality fault localizations.  When applied to non-compiler
faults, the metric tended to either not produce a localization,
produce a very small incorrect localization (1-3 statements), or
produce a very high quality localization.  Restricting to the cases
where we consider {\bf Repair} applicable (7 faults) {\bf Repair}
perfectly localized 4 of them, and produced a 1 or 2 statement
incorrect localization for the others.

@@

{\scriptsize {\bf Acknowledgements:} The authors would like to thank the authors of
the MUSEUM \cite{multilingual} and Metallaxis-FL vs. MUSE 
\cite{Papadakis} studies for access to their data sets.  In
particular, we thank Shin Hong and Thierry Chekam for prompt
assistance beyond the call of duty.  We would like to thank the
authors of the Semantic Crash Bucketing \cite{SCB} study, in
particular Rijnard van Tonder and Claire Le Goues, for their assistance in
comparing our results with SCB.

>>>>

\section{Conclusions and Future Work}
\label{conc}
When are two failing test cases due to the same fault?  This paper
demonstrates that
``when they are repaired by the same program mutants'' is a useful answer to
this question.  The problem of causality in executions is hard, and
has long been tied to a notion of similarity of
executions \cite{NearNeighbor,GroceError}.  By using program changes
(produced by mutants) as
causes to determine distance, it is possible to improve on efforts
to identify the set of faults in a large set of redundant compiler failures
\cite{PLDI13} and discover the source code locations of faults
\cite{MUSE,multilingual}.  For a set of more than 2,800 tests and more
than 50 faults, over the Mozilla SpiderMonkey 1.6 JavaScript compiler and
GCC 4.3.0, our methods improve fault identification (``fuzzer taming''), in a statistically significant way
(with effect size of about 3\% improvement), over
the \emph{best} (for each subject program) of over 16 metrics
considered in previous work.

We also demonstrated that our approach can be cheap and effective in
fuzzer taming not targeting compilers.  It performed much better than
a coverage-based ranking approach, reliably revealing distinct faults
in the first few inputs presented, and is more general in application
than the (to our knowledge) best competing method, semantic crash
bucketing \cite{SCB}.

Preliminary investigation also shows improvement (for a shared
mutation testing budget) over previous mutant-based fault localization
methods, for the same tests and a subset of 24 faults with known
locations.  Our {\bf Repair} method, in particular, was the only
localization approach to provide any perfect localizations of faults
(it produced 3),
and provided three times as many very-high-quality (ranking the fault
in top 5 locations) localizations as the next best method
\cite{multilingual}  --- 6 such localizations, compared to only 2.
For GCC wrong-code faults, only our methods produced any
very-high-quality fault localizations.  When applied to non-compiler
faults, the metric tended to either not produce a localization,
produce a very small incorrect localization (1-3 statements), or
produce a very high quality localization.  Restricting to the cases
where we consider {\bf Repair} applicable (7 faults) {\bf Repair}
perfectly localized 4 of them, and produced a 1 or 2 statement
incorrect localization for the others.

@@

{\scriptsize {\bf Acknowledgements:} The authors would like to thank the authors of
the MUSEUM \cite{multilingual} and Metallaxis-FL vs. MUSE 
\cite{Papadakis} studies for access to their data sets.  In
particular, we thank Shin Hong and Thierry Chekam for prompt
assistance beyond the call of duty.  We would like to thank the
authors of the Semantic Crash Bucketing \cite{SCB} study, in
particular Rijnard van Tonder and Claire Le Goues, for their assistance in
comparing our results with SCB.}

### 2019-09-21 journal/experiments.tex
much more

  These crashes exhibit a classic fuzzer taming structure.  Three of the bugs are easy to identify: they are triggered by 15, 14, and 11 of the 38 AFL-produced crashing inputs, respectively, and all have multiple inputs that uniquely detect that bug, and no other.  The fourth bug, however, is only triggered by \emph{three} of the 38 inputs, and is never uniquely present (any input triggering it also triggers at least one other bug).  This bug was only found by AFL after more than an hour of fuzzing, in fact.

@@

>>>>

  These crashes exhibit a classic fuzzer taming structure.  Three of the bugs are easy to identify: they are triggered by 15, 14, and 11 of the 38 AFL-produced crashing inputs, respectively, and all have multiple inputs that uniquely detect that bug, and no other.  The fourth bug, however, is only triggered by \emph{three} of the 38 inputs, and is never uniquely present (any input triggering it also triggers at least one other bug).  The bug frees a pointer that can subsequently be used, and it is (as often with use-after-frees \cite{DangSan}) hard to produce inputs that actually cause this to happen. This bug was only found by AFL after nearly an hour of fuzzing, in fact.

@@

To our knowledge, the state-of-the-art in research on advancing fuzzing triage over the tools built into fuzzers like AFL is represented by the \emph{semantic crash bucketing} (SCB) approach of van Tonder, Kotheimer, and Le Goues \cite{SCB}.  This approach uses patch templates based on common types of bugs/semi-fixes, combined with semantic information obtained by observing the execution of a crashing input, to bucket crashing inputs discovered by fuzzers.  We contacted the SCB authors, and with their cooperation investigated how well SCB handled the fuzzgoat crashes.  The fuzzgoat code highlights the primary limitation of SCB: namely, if a kind of failure is not handled by a (manually constructed) patch template and identified by the semantic feedback mechanisms, then SCB does not really handle it.  The SCB tool was able to produce a patch for one of the four fuzzgoat bugs, a null pointer dereference.  Unfortunately, at present, SCB does not handle bugs related to misuse of {\tt free} (use-after-free, double frees, or frees of invalid pointers), and the other three fuzzgoat bugs are all {\tt free}-related.  SCB therefore can very effectively identify the inputs associated with one of the four bugs (when it is the only one triggeered by the input), but provides no assistance with finding the other three bugs. This is not to say that SCB is useless here; the null pointer bug alone is responsible for 13 of the 38 crashes, so SCB does make it easy to see one example of the null pointer bug, and ignore another 12 inputs.  It does not, however, help find the rare bug with only a few instances among the remaining 25 inputs.  While mutation repair also has no knowledge of {\tt free} bugs, it is able to find mutants that avoid their symptoms or their causes, and thus triage all four faults effectively.   The SCB team added the fuzzgoat example to their published VM, and plan to use it to drive development of patch templates and analysis for use-after-frees; this will, at some point, likely make it possible for SCB to handle fuzzgoat effectively.  However, in the long term, if fuzzing is applied to find assertion violations, differential testing divergences \cite{Differential,ICSEDiff}, or other more complex ``custom'' properties, as is likely with the appearance of tools such as DeepState \cite{DeepState} that merge fuzzing and property-based testing, it is hard to see how SCB will handle these ``custom'' bug types.

Fuzzgoat is a poor candidate for fault localization, due to the lack of a reasonable set of passing tests, and due to the fact that all four bugs are fairly easy to understand once an appropriate input is run under a sanitizer.  We do note that repair manages to localize the null pointer dereference perfectly (SCB's patch is also an excellent localization for this bug).  Given passing tests, we suspect all fault localization methods discussed in this paper could handle the localization problem easily, in contrast to a typical compiler bug.

### 2019-09-21 journal/relatedwork.tex
much more

>>>>

Explaining, rather than merely localizing, bugs is a less common goal, though all mutation-based approaches can probably be adapted to this idea (since a mutation is, itself, a kind of explanation).  Key work on explaining bugs in addition to localizing them includes Groce's early model-checking work \cite{GroceError,ChakiLev} and the MintHint \cite{MintHint} approach, which bears some resemblance to the use of mutants as ``hints'' for fault repair, but is more general and backed by user studies to show its utility.  The real-world value of MintHint explanations supports the idea that mutant-based explanations might be useful to developers.
